### 2016-06-01 lineups.Rnw
fiddling with the node labelling

set.seed(12345) 
ggplot(data = jTT, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='grey80',vjust = 0, hjust =0, arrowgap = .15, colour = 'black', size=10) + 
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  theme_net() +
  theme(legend.position = "none")
@
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Doubly achieved distance between actors $i$ and $k$.}
<<dab, echo=FALSE, fig.width=2, fig.height=2, message = FALSE, warning = FALSE, fig.align='center'>>=
dade <- data.frame(from = c('i', 'i', 'h', 'j'), to = c('h', 'j', 'k', 'k'))
dadn <- data.frame(id = letters[8:11], group = c(1,1,1,1))

@@

set.seed(12345) 
ggplot(data = dad, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='grey80',vjust = 0, hjust =0, arrowgap = .15, colour = 'black', size=10) + 
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  theme_net() +
  theme(legend.position = "none")
@
\end{subfigure}
\caption{\label{fig:structures}Structural newtwork effects. On the left, a jumping transitive triplet (JTT). On the right, a doubly achieved distance between $i$ and $k$.}
\end{figure}

>>>>

set.seed(12345) 
ggplot(data = jTT, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='grey80',vjust = 0.5, hjust =0.5, arrowgap = .15, colour = 'black', size=10) + 
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  theme_net() +
  theme(legend.position = "none")
@
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Doubly achieved distance between actors $i$ and $k$.}
<<dab, echo=FALSE, fig.width=2, fig.height=2, message = FALSE, warning = FALSE, fig.align='center'>>=
dade <- data.frame(from = c('i', 'i', 'h', 'j'), to = c('h', 'j', 'k', 'k'))
dadn <- data.frame(id = letters[8:11], group = c(1,1,1,1))

@@

set.seed(12345) 
ggplot(data = dad, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='grey80',vjust = 0.5, hjust =0.5, arrowgap = .15, colour = 'black', size=10) + 
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  theme_net() +
  theme(legend.position = "none")
@
\end{subfigure}
\caption{\label{fig:structures}Structural newtwork effects. On the left, a jumping transitive triplet (JTT). On the right, a doubly achieved distance between $i$ and $k$.}
\end{figure}
